---
title: "Installation and Use of the Graduate School Reports Shiny App"
author: "Ben Barnard"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation and Use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The purpose of this package vignette is to walk through the installation and running of the Graduate School Reports Shiny application for running locally on your computer.

## 1. Installation of Latex typesetting Language

First, we will downlaod and install the Latex typesetting language. The reports are not written in Latex but markdown but the latex language is need for some special figures and functions in the reports. To download latex first we must determine if you are using a Windows, Mac, or Linux machine. If you are using a Windows machine you will have to download MikTex found at http://miktex.org/. If you are using a Mac machine you will have to download MacTex found at https://tug.org/mactex/. If you are using a Linux machine you will have to download Tex Live found at http://www.tug.org/texlive/. Once your distribution has been downloaded which could take a while since they are big files you will run the typical installation. Do not select any custom options since these might have unknown repercussions. 

## 2. Installation of R statistical language

Next, we will have to install the current version of R. R is a statistical programming language that has slowly become the most popular statistical language and is built for data manipulation and analysis. The Shiny app itself is built in the R language. We can download the most current version of R at https://www.r-project.org/. Only the base installation is needed for our Shiny app. Once downlaoded install the R language with the default options. Customizing your installation could lead to unforseen problems.

## 3. Installation of devtools and GradSchoolReport packages

Now that we have R and Latex installed we will install the devtools and GradSchoolReport packages. We can install the devtools package by running R code below.

```{r, eval = FALSE}
install.packages("devtools")
```

Then, to install GradSchoolReport we with have to run the code below.

```{r, eval = FALSE}
devtools::install_github("BenBarnard/GradSchoolReport")
```

## 4. Run Shiny App

Finally, we can now run our Shiny app with the line of code below.

```{r, eval = FALSE}
GradSchoolReport::runGradSchoolApp()
```
